The forestecology R package for fitting and assessing models of interspecies competitive effects on the growth of trees

### 2021-03-03 paper/forestecology.Rmd
renamed all cv_grid_sf object names to blocks

```{r scbi-focal-vs-comp}
# TODO: Below reconcile the number of rows as they off by one from growth_scbi %>% 
# filter(!is.na(growth) & !buffer). Perhaps by removing NA's in the growth_scbi stage?
focal_vs_comp_scbi <- growth_scbi %>%
  create_focal_vs_comp(comp_dist, cv_grid_sf = blocks_scbi, id = "stemID")
focal_vs_comp_scbi %>% 
  select(-foldID)
```

>>>>

```{r scbi-focal-vs-comp}
# TODO: Below reconcile the number of rows as they off by one from growth_scbi %>% 
# filter(!is.na(growth) & !buffer). Perhaps by removing NA's in the growth_scbi stage?
focal_vs_comp_scbi <- growth_scbi %>%
  create_focal_vs_comp(comp_dist, blocks = blocks_scbi, id = "stemID")
focal_vs_comp_scbi %>% 
  select(-foldID)
```
